---
title: "Penguin_assignment"
output:
  pdf_document: default
  html_document: default
date: "2022-12-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Firstly load all relevent packages and import the data set

```{r}
install.packages("palmerpenguins")

install.packages("ragg")
install.packages("svglite")
library(palmerpenguins)
library(ggplot2)
suppressPackageStartupMessages(library(janitor))
suppressPackageStartupMessages(library(dplyr))
library(tidyr)
library(ragg)
library(svglite)

setwd("C:/Users/Public/Documents/reproducible_data_science")
write.csv(penguins,(file = "C:/Users/Public/Documents/reproducible_data_science/penguins"))

head(penguins)
penguins <- read.csv("C:/Users/Public/Documents/reproducible_data_science/penguins")
```

Now we implement our data cleaning code, this can be done in another R file but in this case im doing it within the same code file

```{r}
data_cleaning <-  function(data_raw){
  data_raw %>%
    clean_names %>%
    remove_empty(c("rows", "cols")) %>%
    select(-starts_with("delta")) %>%
    select(-comments)
}  
```

now we remove any bill length NA's

```{r}
remove_empty_flipper_length <- function(data_clean){
  data_clean %>%
    filter(!is.na(flipper_length_mm)) %>%
    select(species, flipper_length_mm)
}
```

Now we run a statistical test, in this case a linear regression to see if body mass correlates with flipper length across each species individually.

```{r}
mod1 <- lm(body_mass_g ~ flipper_length_mm + species, penguins)
summary(mod1)


plot(body_mass_g ~ flipper_length_mm, data=penguins, col = species)
  


```

from this we can conclude that flipper length dose correlate with body mass with high certainty across all species
