---
title: "Penguin_assignment"
output:
  pdf_document: default
  html_document: default
date: "2022-12-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Firstly load all relevant packages and import the data set

```{r}
install.packages("palmerpenguins")

install.packages("ragg")
install.packages("svglite")
library(palmerpenguins)
library(ggplot2)
suppressPackageStartupMessages(library(janitor))
suppressPackageStartupMessages(library(dplyr))
library(tidyr)
library(ragg)
library(svglite)

setwd("C:/Users/Public/Documents/reproducible_data_science")
write.csv(penguins,(file = "C:/Users/Public/Documents/reproducible_data_science/penguins"))

head(penguins)
penguins <- read.csv("C:/Users/Public/Documents/reproducible_data_science/penguins")
```

Now we implement our data cleaning code, this can be done in another R file but in this case i'm doing it within the same code file. This code simply removes all empty rows and columns as well as any that start with delta as they are not relevent. Comments are also removed as they are not relevant 

```{r}
data_cleaning <-  function(data_raw){
  data_raw %>%
    clean_names %>%
    remove_empty(c("rows", "cols")) %>%
    select(-starts_with("delta")) %>%
    select(-comments)
}  
```

now we remove any penguins that have NA vlaue for flipper length as they will not be relevent to our study.

```{r}
remove_empty_flipper_length <- function(data_clean){
  data_clean %>%
    filter(!is.na(flipper_length_mm)) %>%
    select(species, flipper_length_mm)
}
```

Now we run a statistical test, in this case a linear regression to see if body mass correlates with flipper length across each species individually.

```{r}
mod1 <- lm(body_mass_g ~ flipper_length_mm + species, penguins)
summary(mod1)


plot(body_mass_g ~ flipper_length_mm, data=penguins, col = species)
  


```

From this we can conclude that flipper length dose correlate with body mass with high certainty across all species
